### 2020-06-12 Report/aws_325ghz_study.tex
added stats for T_rec = 1800, and T_rec = 2400

\subsection{Application of correction scheme to AWS-32, AWS-33, AWS-35 and AWS-36}
%
The correction scheme can also be extended to other combinations of 183GHz and
325GHz channels. The most relevant combinations for clear-sky screening are: AWS-32 and
AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.

@@

\subsubsection{Training}
%  
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz. A separate QRNN is used for each of the 183\,GHz channels. For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz. We assess the performance of the scheme using both three channel and four channel options of 325\,GHz. Two configurations for three channel option are described in Sec.~\ref{sec:}, and both have been used to train QRNN separately. Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option. Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".

@@

The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance. 
%
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
	\label{fig:quantile_loss}
\end{figure}
%
\subsection{Prediction accuracy}
%
We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset. Noise is added to each simulation to mimic a new measurement dataset.

@@

Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz. Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out. Both the three channel and four channel QRNN model are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric. The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}. . The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''. For AWS-34, the predictions from all three QRNN models are comparable.

\begin{figure}[!tb]
	\centering
	\includegraphics[height=60mm]{distribution_predicted_C32}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C33}
	\includegraphics[height=60mm]{distribution_predicted_C34}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C35}
	\includegraphics[height=60mm]{distribution_predicted_C36}
	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.  }
	\label{fig:pdf:qrnn}
\end{figure}

@@

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\

		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}}
	\label{tab:qrnn:C34}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       & -0.004 & 0.450 &             -0.030 &      - \\
uncorrected                 & -1.343 & 5.908 &             -7.484 &      - \\
corrected (three-a)  		&  0.019 & 0.889 &             -3.519 &      4.906 \\	 
corrected (three-b)  		& -0.008 & 0.850 &             -3.326 &      4.926 \\			
corrected (four)    		& -0.011 & 0.878 &             -3.030 &      4.930 \\

		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
	\label{tab:qrnn:C32}
\end{table}

@@

\subsection{Uncertainty estimation}
%
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{prediction_uncertainty.png}
	\caption{The prediction uncertainty with respect to quantiles for randomly selected 2400 cases.}
	\label{fig:prediction_uncertainty}
\end{figure}

@@

\subsection{229 vs.\ 325\,GHz}

\subsubsection{Altitude coverage}
%
This discussion is based on figures and text found in Sec.~\ref{sec:overview}.
A basic remark is that a channel at 229\,GHz channel has a lower sounding
altitude than all the 183\,GHz channels for clear-sky conditions. Accordingly,
there are no matching RH weighting functions between 229\,GHz and 183\,GHz
channels. On the other hand, channels around 325\,GHz have quite similar
characteristics as some of the 183\,GHz channels (for clear-sky), but
consistently have a sounding altitude above the one of AWS-32.

@@

>>>>

\subsection{Application of correction scheme to AWS-32, AWS-33, AWS-35 and AWS-36}
%

The correction scheme can also be extended to other combinations of 183GHz and
325GHz channels. The most relevant combinations for clear-sky screening are: AWS-32 and
AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.

@@

\subsubsection{Training}
%  
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
	\label{fig:quantile_loss}
\end{figure}
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz. A separate QRNN is used for each of the 183\,GHz channels. For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz. We assess the performance of the scheme using both three channel and four channel options of 325\,GHz. Two configurations for three channel option are described in Sec.~\ref{sec:}, and both have been used to train QRNN separately. Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option. Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".

@@

The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance. 
%

%
\subsection{Prediction accuracy}
%
\begin{figure}[!p]
	\centering
	\includegraphics[height=60mm]{distribution_predicted_C32}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C33}
	\includegraphics[height=60mm]{distribution_predicted_C34}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C35}
	\includegraphics[height=60mm]{distribution_predicted_C36}
	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.  }
	\label{fig:pdf:qrnn}
\end{figure}
We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset. Noise is added to each simulation to mimic a new measurement dataset.

@@

In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Section~\ref{sec:}. Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz. Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out. Both the three channel and four channel QRNN model are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric. The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}. . The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''. For AWS-34, average deviation in the predictions from all three QRNN models are comparable.  The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.32), however with QRNN the skewness is largely reduced and the symmetry in the distributions is reflected in the low skewness values. Among the three set of predictions, option three-b has the most symmetric error distribution but with a relatively large spread. Predictions from option four have the lowest standard deviation (0.620\,K), which is interestingly smaller than the standard deviation of noise (0.641\,K). Though, all three options of 325\,GHz provide a full coverage to the hydrometer impact in AWS-34, predictions from four channel option are slightly more accurate.

Similar error statistics are also estimated for other 183\,GHz channels. Table~\ref{tab:qrnn:C32} provides the statistics for AWS-32. Before correction, the average bias and standard deviation with respect to noise free simulations is -1.343\,K and 5.908\,K respectively. However, after correction(four channel), the bias and standard deviation are -0.011\,K and 0.878\,K. The skewness in the error distributions is also reduced in the predictions (from -7.48 to -3.03). But a relatively high negative skewness in the predicted dataset indicates presence of uncorrected cloud impact.

Table~\ref{tab:qrnn:C33} shows the statistics for AWS-33. The standard deviation in the four channel option (0.591\,K) is slighly lower than three-b(0.612\,K), but the skewness in three-b in lower. This indicates that with four channel option, the QRNN predictions are mostly closer to the simulations, but few cases with large cloud impact are under predicted.

For AWS-35 (Table~\ref{tab:qrnn:C35}), the four channel option has the best performance. The average bias in QRNN predictions (four) is only 0.04\,K in comparsion to -0.42\,K for the measurements. Option three-b has lower skewness than option four, but the standard deviation is higher. It is interesting to note that the standard deviation in all three predicted datasets is always lower than noise. Similar results are also seen for AWS-36 (Table~\ref{tab:qrnn:C36}). The four channel combination reduces the average bias from -0.269\,K to 0.056\,K and the standard deviation from 2.059\,K to 0.779\,K. Also for this channel, the spread of the predictions is narrower than noise.

@@

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}}
	\label{tab:qrnn:C34}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       & -0.004 & 0.450 &             -0.030 &      - \\
uncorrected                 & -1.343 & 5.908 &             -7.484 &      - \\
corrected (three-a)  		&  0.019 & 0.889 &             -3.519 &      4.906 \\	 
corrected (three-b)  		& -0.008 & 0.850 &             -3.326 &      4.926 \\			
corrected (four)    		& -0.011 & 0.878 &             -3.030 &      4.930 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
	\label{tab:qrnn:C32}
\end{table}

@@

\subsection{Uncertainty estimation}
%

\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{prediction_uncertainty.png}
	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases. The red line represents the uncertainty if underlying distribution is purely Gaussian with standard deviation 0.62\,K. }
	\label{fig:prediction_uncertainty}
\end{figure}

\section{Sensitivity to different receiver noise temperatures}

\subsection{T rec = 1800}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.451 &              0.020 &      0.000 \\
	uncorrected                & -1.342 & 5.908 &             -7.479 &      0.000 \\
	corrected (three channela) & -0.009 & 0.893 &             -3.092 &      4.990 \\
    corrected (three channelb) &  0.009 & 0.888 &             -3.197 &      4.902 \\	
	corrected (four channel)   &  0.006 & 0.860 &             -2.943 &      4.954 \\
		\hline
	\end{tabular}
	\caption{ AWS-32 , Trec = 1800}
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.452 &              0.015 &      0.000 \\
	uncorrected                & -0.975 & 4.703 &             -8.763 &      0.000 \\
	corrected (three channela) &  0.085 & 0.587 &             -0.640 &      4.209 \\
	corrected (three channelb) &  0.062 & 0.605 &             -0.845 &      4.205 \\
	corrected (four channel)   &  0.048 & 0.606 &             -1.112 &      4.264 \\
		\hline
	\end{tabular}
	\caption{ AWS-33, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      &  0.001 & 0.632 &              0.021 &      0.000 \\
	uncorrected                & -0.676 & 3.686 &            -10.301 &      0.000 \\
	corrected (three channela) &  0.079 & 0.646 &             -0.344 &      2.730 \\
    corrected (three channelb) &  0.090 & 0.639 &             -0.405 &      2.582 \\
	corrected (four channel)   &  0.079 & 0.630 &             -0.399 &      2.981 \\
		\hline
	\end{tabular}
	\caption{ AWS-34, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.001 & 0.629 &              0.007 &      0.000 \\
uncorrected                 & -0.417 & 2.654 &            -12.446 &      0.000 \\
corrected (three channela)  &  0.045 & 0.636 &             -0.188 &      1.431 \\
corrected (three channelb)  &  0.081 & 0.640 &             -0.458 &      1.299 \\
corrected (four channel)    &  0.058 & 0.617 &             -0.007 &      1.801 \\
		\hline
	\end{tabular}
	\caption{ AWS-35, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      &  0.002 & 0.882 &             -0.006 &      0.000 \\
uncorrected                & -0.268 & 2.063 &            -12.003 &      0.000 \\
corrected (three channela) &  0.075 & 0.831 &             -0.130 &      1.283 \\
corrected (three channelb) &  0.105 & 0.807 &             -0.080 &      1.136 \\
corrected (four channel)   &  0.093 & 0.826 &             -0.175 &      1.120 \\
		\hline
	\end{tabular}
	\caption{ AWS-36, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\subsection{T rec = 2400}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.002 & 0.454 &              0.003 &      0.000 \\
uncorrected                 & -1.343 & 5.907 &             -7.483 &      0.000 \\
corrected (three channela)  & -0.017 & 0.877 &             -3.381 &      4.934 \\
corrected (three channelb)  & -0.015 & 0.882 &             -3.177 &      4.974 \\
corrected (four channel)    &  0.028 & 0.876 &             -3.638 &      4.978 \\
		\hline
	\end{tabular}
	\caption{ AWS-32, Trec = 2400 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise                     & -0.003 & 0.448 &              0.005 &      0.000 \\
uncorrected                & -0.979 & 4.709 &             -8.762 &      0.000 \\
corrected (three channela) &  0.057 & 0.628 &             -0.728 &      4.232 \\
corrected (three channelb) &  0.040 & 0.614 &             -0.786 &      4.205 \\
corrected (four channel)   &  0.043 & 0.614 &             -0.798 &      4.232 \\
		\hline
	\end{tabular}
	\caption{ AWS-33, Trec = 2400  }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise                      & -0.001 & 0.638 &              0.006 &      0.000 \\
uncorrected                 & -0.676 & 3.688 &            -10.299 &      0.000 \\
 corrected (three channela) &  0.069 & 0.655 &             -0.396 &      2.666 \\
corrected (three channelb)  &  0.090 & 0.648 &             -0.310 &      2.594 \\
corrected (four channel)    &  0.059 & 0.643 &             -0.340 &      2.937 \\
		\hline
	\end{tabular}
	\caption{ AWS-34, Trec = 2400 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      & -0.004 & 0.633 &              0.021 &      0.000 \\
uncorrected                & -0.420 & 2.654 &            -12.449 &      0.000 \\
corrected (three channela) &  0.034 & 0.646 &             -0.389 &      1.479 \\
corrected (three channelb) &  0.076 & 0.647 &             -0.148 &      1.291 \\
corrected (four channel)   &  0.044 & 0.632 &             -0.188 &      1.809 \\
		\hline
	\end{tabular}
	\caption{ AWS-35, Trec = 2400}
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      &  0.005 & 0.884 &             -0.026 &      0.000 \\
uncorrected                & -0.268 & 2.057 &            -11.977 &      0.000 \\
corrected (three channela) &  0.039 & 0.854 &             -0.131 &      1.283 \\
corrected (three channelb) &  0.090 & 0.839 &             -0.096 &      1.108 \\
corrected (four channel)   &  0.059 & 0.850 &             -0.140 &      1.140 \\
		\hline
	\end{tabular}
	\caption{ AWS-36, Trec = 2400 }
	\label{tab:qrnn:C36}
\end{table}

@@

\subsection{229 vs.\ 325\,GHz}
\subsubsection{Altitude coverage}
%
This discussion is based on figures and text found in Sec.~\ref{sec:overview}.
A basic remark is that a channel at 229\,GHz channel has a lower sounding
altitude than all the 183\,GHz channels for clear-sky conditions. Accordingly,
there are no matching RH weighting functions between 229\,GHz and 183\,GHz
channels. On the other hand, channels around 325\,GHz have quite similar
characteristics as some of the 183\,GHz channels (for clear-sky), but
consistently have a sounding altitude above the one of AWS-32.

@@

\subsection{Performance of QRNN}
%
\dots
